Dummy classifier

### 2020-12-01 src/dummy_classifier.Rmd
Dummy model is now logistic regression, and predicts test data

```{r}
load("~/FRCBS/interval-sims/rf-train-and-validate-datas.rdata", verbose=TRUE)
```

@@

dummy_predictor <- function(df, Hb_threshold=NULL) {
  if (is.null(Hb_threshold)) {    # use -previous_Hb as score
    result <- tibble(Deferred = -df$previous_Hb,
                     obs = df$Hb_deferral)
  } else {                        # use logistic function of previous_Hb as score
    result <- tibble(Deferred = score(df$previous_Hb, Hb_threshold), 
                     obs = df$Hb_deferral)

@@

@@

```{r}
train_female <- train %>% filter(gender=="Women")
train_male <- train %>% filter(gender=="Men")
validate_female <- validate %>% filter(gender=="Women")
validate_male <- validate %>% filter(gender=="Men")
```

@@

```{r}
prediction_female <- dummy_predictor(validate_female, 125)  # or would mean Hb be better centering point than deferral threshold
prediction_male <- dummy_predictor(validate_male, 135)

head(prediction_female)
head(prediction_male)
```

```{r}
save(prediction_female, file="~/FRCBS/interval-sims/progesa-validate-female-dummy.rdata")
save(prediction_male, file="~/FRCBS/interval-sims/progesa-validate-male-dummy.rdata")
```

```{r}
dummy_result <- process_all_data(dummy2_ids)
```

```{r}
dummy_result
```

@@

```{r}
roc_male <- roc_wrapper(prediction_male)
pr_male <- pr_wrapper(prediction_male)
```

```{r}
v <- c(roc_female$roc$ci[c(2,1,3)], pr_female$ci[c(1,2,3)], 
       roc_male$roc$ci[c(2,1,3)], pr_male$ci[c(1,2,3)])
aucs <- as_tibble(matrix(v, ncol=6, byrow=TRUE))
colnames(aucs) <- c("AUROC", "AUROC low", "AUROC high", "AUPR value", "AUPR low", "AUPR high")
aucs <- aucs %>% 
  mutate(Id=dummy2_ids) %>%
  select(Id, everything())

aucs
```

```{r}
dummy_result <- inner_join(aucs, dummy_result, by="Id")
dummy_result
```

>>>>

```{r}
load("~/FRCBS/interval-sims/rf-train-and-validate-datas.rdata", verbose=TRUE)  # returns train and validate dataframes
load("~/FRCBS/interval-sims/rf-test-data.rdata", verbose=TRUE) # returns test dataframe
```

@@

dummy_predictor <- function(df, Hb_threshold=NULL) { # fake logistic regression
  if (is.null(Hb_threshold)) {    # use -previous_Hb as score
    result <- tibble(Deferred = -df$previous_Hb,
                     obs = df$Hb_deferral)
  } else {                        # use logistic function of previous_Hb as score
    result <- tibble(Deferred = score(df$previous_Hb, Hb_threshold), 
                     obs = df$Hb_deferral)

@@

dummy_predictor2 <- function(train, validate) {  # real logistic regression
  glm.fit <- glm(Hb_deferral ~ previous_Hb,
               data = train,
               family = binomial)

  print(glm.fit)

  glm.probs <- predict(glm.fit,
                      newdata = validate,
                      type = "response")

  result <- tibble(Deferred = glm.probs, 
                   obs = validate$Hb_deferral)

  return(result)  
}

@@

```{r}
train_female <- train %>% filter(gender=="Women")
train_male <- train %>% filter(gender=="Men")
validate_female <- validate %>% filter(gender=="Women")
validate_male <- validate %>% filter(gender=="Men")
test_female <- test %>% filter(gender=="Women")
test_male <- test %>% filter(gender=="Men")
```

@@

```{r}
use_logistic_regression=TRUE
if (use_logistic_regression) {
  prediction_female <- dummy_predictor2(train_female, test_female)  # or would mean Hb be better centering point than deferral threshold
  prediction_male <- dummy_predictor2(train_male, test_male)
} else {
  prediction_female <- dummy_predictor(validate_female, 125)  # or would mean Hb be better centering point than deferral threshold
  prediction_male <- dummy_predictor(validate_male, 135)
}
head(prediction_female)
head(prediction_male)
```

```{r}
save(prediction_female, file="~/FRCBS/interval-sims/progesa-validate-female-dummy2.rdata")
save(prediction_male, file="~/FRCBS/interval-sims/progesa-validate-male-dummy2.rdata")
```

```{r}
dummy_result <- process_all_data(dummy2_ids, replicates=100)
```

```{r}
df <- dummy_result %>% 
  pivot_wider(names_from=c("variable", "type"), values_from=value, names_glue="{variable} {type}")
names(df) <- str_remove(names(df), " value$")
df <- df %>%
  select("Id", "F1", "F1 low", "F1 high", "threshold6", "threshold12", "E6", "E6 low", "E6 high", "E12", "E12 low", "E12 high")

df
```

@@

```{r}
roc_male <- roc_wrapper(prediction_male)
pr_male <- pr_wrapper(prediction_male)
```
```{r}
roc_female
pr_female
roc_male
pr_male
```

```{r}
# v <- c(roc_female$roc$ci[c(2,1,3)], pr_female$ci[c(1,2,3)], 
#        roc_male$roc$ci[c(2,1,3)], pr_male$ci[c(1,2,3)])
# aucs <- as_tibble(matrix(v, ncol=6, byrow=TRUE))
# colnames(aucs) <- c("AUROC", "AUROC low", "AUROC high", "AUPR value", "AUPR low", "AUPR high")
# aucs <- aucs %>% 
#   mutate(Id=dummy2_ids) %>%
#   select(Id, everything())
# 
# aucs
```

```{r}
# dummy_result <- inner_join(aucs, dummy_result, by="Id")
# dummy_result
```
